
% DISPOSISJON
% 	Intro: Begynn beldig vidt: "neuron" er en samlebetegnelse for en spesiell type celler med signalling properties (kan bli eksitert). [REF].
%  		IDE: -> Skriv litt om at den vide grupperingen gjør at simulering er vanskelig (men ikkje her: MEN i ANN-seciton!)
%  		- Dette ligger i komplekse neurale nettvert med "recurrent connections" og høg grad av 'connectivity'.(I CNS er det estimert til å være 1000+ input per neuron)
% 		- Koblingen mellom 
% 




% "Although the human brain contains an extraordinary number of these cells (in the order 10E11 neurons), which can be classified into at least a thousand different types, all nerve cells share the same architecture." Kandell kap 2.



\section{Biological Neural Systems}
	
	In the late 1800s, Camillo Golgi developed a way of staining nervous tissue so that complex networks of nerve cells (neurons) became apperent.
	Ramon Y Cajal, Santiago used Golgi's technique in such a way that individual neurons could be separated, and it was observed that nervous tissue was not a continuous web but a network of discrete cells. 
	He proposed what has later been known as the neuron doctrine; That the basis of intelligence is individual ``brain cells'' that can process incoming transmissions and send ouput transmissions in certain situations.
	For their contribution, Ramon Y Cajal and Golgi shared the 1906 Nobel's price in Physiology and Medicine. %CITE: Kandell kap 2. 

	Modern neuroscience follows the neuron doctrine. 
	Each node in a neural network is called a neuron and the connection between neurons are called synapses.
	All synapses have direction(propagates information in one direction) and transmitts if the presynaptic neuron ``fires'' an action potential.
	Synapses can be exitatory or inhibitory.
	Transmissions in excitatory synapses increase the postsynaptic membrane potential, causing that neuron to approach firing. %sending an action potential.
	Inhibitory transmissions does the opposite, and inhibits the postsynaptic neuron with respect to firing.
	When a neuron fires an action potential, a transmission is initialized for all the neuron's output synapses.  % redundant? eller viktig å poengtere?
% TODO TODO TODO CITE!
	
	In this section, the most important elements of neural signal processing are presented, enabling the reader to become more familiar with how neural networks process information.
	%It is recommended that the reader utilize this section as a reference work when neural simulation is discussed.
	It is recommended that the reader utilize this section as a reference work when different methods of neural simulation is presented.
	Before discussing how the neuron processes information, the organization of the neuron have to be reviewed. %REVIEWED er dårlig TODO
	%We will start with the organization of the neuron, before moving on to a fundamental signal processing mechanism of the neuron; The electrochemical properties of the neuron membrane.




%	The most important elements of signal processing in neural systems is presented in this section,
%		enabling the reader to become familiar with how biological neural networks function.
%	Fundamental elements for the neural signal processing is presented, and it is recommended to use this section as a work of reference when 	we later discuss simulating the biological neuron.
																																				%going through the remainder of this text.
	



	

%Using Golgi's technique, Ramon Y Cajal, Santiago stained nervous tissue in such a way that individual neurons could be separated and 

	
	\subsection{The Neuron}
		%TODO TODO TODO TODO Begynn med å beskrive korleis neuronet er (tenk på den figuren eg hadde i FDP). Legg ved figuren.
		% TODO     Etterpå, fortsett som under..
	
		Each neuron is surrouded by a cell membrane with a low permeability to ions, enabling the intracellular fluid to have a different consectration of different ions than the fluid outside the membrane.
		%under: ikkje "spesialiserte", men "dedidkerte"
		All neuron membranes has ionic pumps dedicated to uphold an ionic concentration gradient over the membrane.
		The different ionic pumps push the corresponding ions ``upstream'' in relation to the ionic concentration gradient, resulting in an electrochemical potential over the membrane.
		If specialized ionic gates permeable to certain ions are opened, these ions can flow freely through the gate. % and the neuron membrane is either depolarized of further polarized, depending on which ions are let thought.
		Depending on which ions are let thought, this cause the neuron membrane to either be depolarized of further polarized with respect to the ionic concentration.
		%This cause the neuron membrane to either be depolarized or further polarized with respect to the ionic concentration.
		If the membrane potential becomes more positive than what is referred to as the firing threshold of the neuron, the neuron fires an action potential.
%TODO CITE: Bear kap 3 og 4. F.eks.
%TODO 		Eller: Kandell kap 7,9 (?)
	%FEILAKTIG: Det varierer! (resting pot: mellom neuron, og firing th.: var. i tid)	The membrane potential al rest typically lies around $-65mV$, and the firing threshold is at a more positive membrane potential.

		When a neuron
		%When the membrane potential is above a threshold, an ``action potential'' is fired, and the neuron sends output through all its output synapses.
	



		The neuron is a cell with a special property; It can
			The electrochemical properties of the neurons enables advanced signal processing
			It has the capability of processing signals due to its
			It have electrochemical mechanisms for processing 

		% Membranen - eksiterbar 
		% 
		% 
		% 


	To understand the signalling property of the neuron, 

	\subsection{The Axon and the Action Potential}

	\subsection{The Synapse}

	\subsection{Signal Propagation}
		- oppsymmer AP, spatiotemporal effekt av axon, synaptic transmission, EPSP/IPSP, ...

